Partial Least Squares Regression with Multiple Functional and Scalar Predictors

### 2025-06-29 manuscript/main.tex
start separating the linear system

\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{caption,booktabs,array}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[usenames, dvipsnames]{color}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{rotating}
\usepackage{url}
\usepackage{enumerate}
\allowdisplaybreaks
\usepackage{bbold}
\usepackage{xcolor}         % colors
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}

@@

	Our strategy is to formulate a hybrid random object, 
	by combining   $X$ and $\mathbf{Z}$ into an ordered pair:
	\begin{equation}\label{def:hybid_predictor}
		\mathbf{W} = (X, \mathbf{Z}) 
		\in \mathcal{H},~\text{where}~\mathcal{H}:=\mathcal{F} \times \mathbb{R}^p
	\end{equation}
	An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.  We define the inner product between any two hybrid objects, $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
	\begin{equation}
		\langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} 
		= 
		\langle f_1, f_2\rangle_\mathcal{F} 
		+
		\omega \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k
		+
		\omega \sum \limits_{r=1}^p v_{1r}v_{2r}, 
		\label{eq: hybrid inner product}
	\end{equation}
	with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$. $\omega$ is a positive weight that needs to be pre-specified or estimated. It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}). Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. Then the functional regression model \eqref{eq: functional model} with multiple functional and scalar predictors can be re-expressed in terms of the scalar-on-hybrid regression model as follows
	\begin{equation}
		Y = \langle \boldsymbol{\eta}, \mathbf{W} \rangle_{\mathcal{H}} + \epsilon,
		\label{eq: Hybrid functional model}
	\end{equation}
	where $\boldsymbol{\eta} = (\beta, \boldsymbol{\alpha}) \in \mathcal{H}$ is a hybrid regression coefficient characterizing the association between the hybrid predictor $\mathbf{W}$ and the outcome $Y$.

@@

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}
In practice, the functional predictors $X^{(1)}, \ldots, X^{(K)}$ are not observed as complete curves, but only through their values at a finite set of time points, which may differ across the $K$ predictors. Thus, each observation is represented by a finite-dimensional vector $X_i^{(k)}(\mathbf{t}_k) \in \mathbb{R}^{|\mathbf{t}_k|}$, where $\mathbf{t}_k \subset \mathcal{T}_k$. The first step in functional data analysis typically involves reconstructing the underlying functional form from these discrete measurements, commonly by assuming that sample paths lie in a finite-dimensional space spanned by basis functions.
	\paragraph{Basis functions.}
For $k = 1, \ldots, K$, let $\Phi^{(k)}:= \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$. In our proposed hybrid PLS regression algorithm, this basis system is used to approximate both the predictors and the PLS components. Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting.

	\paragraph{Basis approximation of the hybrid predictor.}	
	For $k = 1, \ldots, K$  and $i = 1, \ldots, n$, 	
	 we approximate each functional predictor within the span of the basis functions $\Phi^{(k)}$ :
\begin{equation*} 
	X_i^{(k)} \approx  \sum_{m=1}^M   c_{im}^{(k)} \phi_m^{(k)} ,
\end{equation*}
where the coefficients $c_{im}^{(k)}$'s satisfy
	\begin{equation*}
	X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} \phi^{(k)}_{m}(t_k)~\text{for all}~t_k \in \mathbf{t}_k \subset \mathcal{T}_k,
\end{equation*}

	The number of basis functions $M$ for each functional predictor can be set to a sufficiently large value (e.g., 15 or 20) to incorporate a rich variety of patterns that functional predictors may exhibit. Note that there is no need to carefully choose different $M$ values for different functional predictors, as an appropriate penalization scheme will be introduced in the later section to regularize each functional predictor to achieve a desired smoothness (see Section \ref{sec: Regularization of PLS Components}).

	\paragraph{Basis approximation of the PLS component.}
	We can also approximate the functional part of the PLS component in terms of the same basis functions: $\psi^{(k)}(t_k) = \sum_{m=1}^M a^{(k)}_{m} b^{(k)}_m(t_k) = \mathbf{a}^{(k)\top} \mathbf{b}^{(k)}(t_k)$ and $\psi(\mathbf{t}) = B(\mathbf{t})^\top \mathbf{a} \in \mathbb{R}^K$, where $\mathbf{a}^{(k)} = (a^{(k)}_{1}, \ldots, a^{(k)}_{M})^\top \in \mathbb{R}^M$, and $\mathbf{a}=(\mathbf{a}^{(1)\top}, \ldots, \mathbf{a}^{(K)\top})^\top \in \mathbb{R}^{MK}$, so that $\boldsymbol{\xi}[\mathbf{t}] = (\psi(\mathbf{t})^\top, \boldsymbol{\theta}^\top)^\top = (\mathbf{a}^\top B(\mathbf{t}), \boldsymbol{\theta}^\top)^\top \in \mathbb{R}^{K+p}$. 
	%
	For each $k = 1, \ldots, K$, let $\mathbf{J}^{(k)} \in \mathbb{R}^{M \times M}$ denote the Gram matrix of the basis functions associated with the $k$-th functional predictor, defined by
	\begin{equation}\label{def:gram_basis}
		\mathbf{J}^{(k)} = \left[ \int_{\mathcal{T}k} b_m^{(k)}(t) \, b_n^{(k)}(t) , dt \right]_{m,n=1}^M.
	\end{equation}
	Using this definition, we construct the following block-diagonal matrices:
	\begin{equation}\label{def:J_and_J_star}
		\mathbf{J} = \mathrm{blkdiag}(\mathbf{J}^{(1)}, \cdots, \mathbf{J}^{(K)}) \in \mathbb{R}^{MK \times MK}~\text{and}~\mathbf{J}^\ast=\mathrm{blkdiag}(\mathbf{J}, \mathbf{I}_p) \in \mathbb{R}^{(MK+p) \times (MK+p)}.
	\end{equation}

@@

We now describe the strategy for computing the PLS direction at the $l$-th iteration. For simplicity, we omit the iteration index and denote the residualized response by $Y$, with finite-sample observations given by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$. Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}} \in \mathbb{R}^{n \times (MK)}$ denote the basis coefficients of its functional part in the finite-sample observations. Our strategy seeks the direction $\boldsymbol{\xi} \in \mathcal{H}$, lying in the span of the basis $B^*[\mathbf{t}]$, that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.

@@

	Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
	\begin{equation*}
		\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
		= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
		=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
	\end{equation*}
	In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
	\begin{proposition} \label{Proposition: property of U}
		The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint. Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in \mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in \mathcal{T}_k$ with $|t_k - t_k^* | < \delta_k$, we have that
		\begin{equation*}
			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
		\end{equation*}
		then $\mathcal{U}$ is a compact operator.
	\end{proposition}
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\boldsymbol{\xi}_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \boldsymbol{\xi}_{(u)} = \kappa_{(u)}  \boldsymbol{\xi}_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
	\begin{proposition}\label{proposition: eigenanalysis}
		\begin{equation*}
			\max \limits_{\substack{\boldsymbol{\xi} \in \mathcal{H} \\ \Vert \boldsymbol{\xi} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)
		\end{equation*}
		is achieved when $\boldsymbol{\xi}$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
	\end{proposition}
	In other words, $l$-th PLS component $\boldsymbol{\xi}_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

	The following proposition states that the PLS components estimated from Proposition  \ref{Proposition: Regularized generalized rayleigh quotient} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
		The estimated PLS components, $\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots, \widehat{\boldsymbol{\xi}}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
		\begin{equation*}
			\langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle 
			= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
			= \mathbb{1}(l=j). 
		\end{equation*}

	Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations. The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
	\begin{proposition}
		The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
		\begin{equation*}
			\widehat{\boldsymbol{\rho}}_l^\top \widehat{\boldsymbol{\rho}}_j= 0 \quad \textnormal{for} \quad \; l,j \in \{1, \ldots, L\}, \; l \ne j. 
		\end{equation*}
		\label{proposition: orthnormality of PLS scores}
	\end{proposition}

@@

	\section{Technical lemmas}

	\section{old notations}

>>>>

\newtheorem{proposition}{Proposition}
\newtheorem{alg}{Algorithm} 
\newtheorem{theorem}{Theorem}
\newtheorem{assumption}{Assumption}
\newtheorem{note}[theorem]{Note}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{define}[theorem]{Definition}
% \newtheorem{denote}[theorem]{denote}
\newtheorem{claim}[theorem]{Claim}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{lemma}{Lemma}
\usepackage{graphicx}
\graphicspath{ {images/} }
\usepackage{amsmath}
\usepackage{mathtools}
\usepackage[flushleft]{threeparttable}
\usepackage[labelfont=bf]{caption}
\usepackage{caption,booktabs,array}
\usepackage{multirow}
\usepackage{makecell}
\usepackage[usenames, dvipsnames]{color}
\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{rotating}
\usepackage{url}
\usepackage{enumerate}
\allowdisplaybreaks
\usepackage{bbold}
\usepackage{xcolor}         % colors
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}

@@

	Our strategy is to formulate a hybrid random object, 
	by combining   $X$ and $\mathbf{Z}$ into an ordered pair:
	\begin{equation}\label{def:hybid_predictor}
		\mathbf{W} = (X, \mathbf{Z}) 
		\in \mathcal{H},~\text{where}~\mathcal{H}:=\mathcal{F} \times \mathbb{R}^p
	\end{equation}
	An alternative notation for the hybrid object can be obtained by evaluating its functional part on $\mathbf{t}$ and expressing it as a $(K+p)$-dimensional vector: $\mathbf{W}[\mathbf{t}] = (X(\mathbf{t}), \mathbf{Z})^\top$, with $ X(\mathbf{t}) = (X^{(1)}(t_1), \ldots, X^{(K)}(t_K))^\top \in \mathbb{R}^K$ and $ \mathbf{Z} = (Z_1, \ldots, Z_p)^\top  \in \mathbb{R}^p$.

	\begin{definition}[Hilbert space of hybrid objects]\label{def:hilbert_space}
		 We define the inner product between any two hybrid objects,
		  $\mathbf{h}_1 = (f_1, \mathbf{v}_1)$ and $\mathbf{h}_2 = (f_2, \mathbf{v}_2)$, as
	\begin{equation}
	\langle \mathbf{h}_1, \mathbf{h}_2\rangle_{\mathcal{H}} 
	:= 
	\langle f_1, f_2\rangle_\mathcal{F} 
	+
	\omega \langle  \mathbf{v_1}, \mathbf{v_2} \rangle = \sum \limits_{k=1}^K \int_{\mathcal{T}_k} f_1^{(k)}(t_k) f_2^{(k)}(t_k) dt_k
	+
	\omega \sum \limits_{r=1}^p v_{1r}v_{2r}, 
	\label{eq: hybrid inner product}
\end{equation}
	with norm $\Vert \cdot \Vert_\mathcal{H} = \langle \cdot,\cdot \rangle_\mathcal{H}^{1/2}$.
		\end{definition}
In \eqref{eq: hybrid inner product}, 
 $\omega$ is a positive weight that needs to be pre-specified or estimated. It is mainly used to take into account heterogeneity between functional and scalar parts in terms of measurement scale and/or amount of variation (see Section \ref{subsec: Data Preprocessing}). Without loss of generality and for the clarity of illustration, all the following theoretical results will be derived for $\omega=1$. The results remain valid for any positive weights. Then the functional regression model \eqref{eq: functional model} with multiple functional and scalar predictors can be re-expressed in terms of the scalar-on-hybrid regression model as follows
	\begin{equation}
		Y = \langle \boldsymbol{\eta}, \mathbf{W} \rangle_{\mathcal{H}} + \epsilon,
		\label{eq: Hybrid functional model}
	\end{equation}
	where $\boldsymbol{\eta} = (\beta, \boldsymbol{\alpha}) \in \mathcal{H}$ is a hybrid regression coefficient characterizing the association between the hybrid predictor $\mathbf{W}$ and the outcome $Y$.

@@

	\subsubsection{Finite-basis approximation of the predictors and regression coefficients}\label{sec: finite basis approximation}
In practice, the functional predictors $X^{(1)}, \ldots, X^{(K)}$ are not observed as complete curves, but only through their values at a finite set of time points, which may differ across the $K$ predictors. Thus, each observation is represented by a finite-dimensional vector $X_i^{(k)}(\mathbf{t}_k) \in \mathbb{R}^{|\mathbf{t}_k|}$, where $\mathbf{t}_k \subset \mathcal{T}_k$. The first step in functional data analysis typically involves reconstructing the underlying functional form from these discrete measurements, commonly by assuming that sample paths lie in a finite-dimensional space spanned by basis functions.

For $k = 1, \ldots, K$, let $\Phi^{(k)}   := \{\phi^{(k)}_1, \ldots, \phi^{(k)}_M\}$, with $M \geq 1$, be an $M$-dimensional basis in $L^2(\mathcal{T}_k)$. In our proposed hybrid PLS regression algorithm, this basis system is used to approximate both the predictors and the PLS components. Additionally, it serves as a regularization mechanism, borrowing strength across components and helping to prevent overfitting. 	The number of basis functions $M$ for each functional predictor can be set to a sufficiently large value (e.g., 15 or 20) to incorporate a rich variety of patterns that functional predictors may exhibit. Note that there is no need to carefully choose different $M$ values for different functional predictors, as an appropriate penalization scheme will be introduced in the later section to regularize each functional predictor to achieve a desired smoothness (see Section \ref{sec: Regularization of PLS Components}).

For $k = 1, \ldots, K$, we project the $k$th functional predictor onto 
$\operatorname{span}(\Phi^{(k)})$:
\begin{equation*}
	X_i^{(k)} \approx \sum_{m=1}^M c_{im}^{(k)} \phi_m^{(k)}, \quad i = 1, \ldots, n,
\end{equation*}
where the coefficients $c_{im}^{(k)}$ satisfy
\begin{equation*}
	X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} \phi_m^{(k)}(t_k), \quad \text{for all } t_k \in \mathbf{t}_k \subset \mathcal{T}_k.
\end{equation*}
Thus, the $n$ observations of the $k$th functional predictor can be represented by an $n \times M$ matrix of coefficients, 	where rows index samples and columns index basis functions:
\begin{equation*}
		\widetilde{\mathbf{C}}^{(k)} := ( c_{im}^{(k)} ).
\end{equation*}

Importantly, the core computation of our algorithm involves the inner product between $n$ hybrid predictor observations and a single hybrid object (the PLS direction), defined via the inner product in Definition \ref{def:hilbert_space}.
 With the basis expansion, this reduces to simple matrix operations. 
For each $k = 1, \ldots, K$, let $\boldsymbol{\Phi}^{(k)} := (\phi^{(k)}_{m \ell })$
denote the	$M \times M$ symmetric matrix with entries  the inner products between basis functions 
\begin{equation}\label{def:gram_basis}
\phi^{(k)}_{m \ell } 
:= 
\langle \phi^{(k)}_m,  \phi^{(k)}_\ell \rangle
=  
\int_{\mathcal{T}_k} \phi^{(k)}_m(t_k) \, \phi^{(k)}_\ell(t_k) \, dt_k.
\end{equation}

\begin{definition}[Hybrid inner product between $n$ observations and a single object]
Let $\boldsymbol{\xi} = (\psi, \mathbf{s}) \in \mathcal{H}$ be a hybrid object with $\psi \in \mathcal{F}$ and $\mathbf{s} \in \mathbb{R}^p$, and let $\mathbf{a}^{(1)}, \ldots, \mathbf{a}^{(K)}$ denote the basis coefficients of $\psi$ with respect to basis $\Phi^{(1)}, \ldots, \Phi^{(K)}$. Then the inner product between $\boldsymbol{\xi}$ and the $n$ basis-approximated hybrid observations $\widetilde{\mathbf{W}}_1, \ldots, \widetilde{\mathbf{W}}_n$, concatenated as a column vector, is denoted $\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}} \in \mathbb{R}^n$ and computed as
	\begin{equation*}
		\langle \widetilde{\mathbf{W}}, \boldsymbol{\xi} \rangle_{\mathcal{H}}
		:=
		\begin{bmatrix}
			\langle \widetilde{\mathbf{W}}_1, \boldsymbol{\xi} \rangle_{\mathcal{H}} \\
			\vdots \\
			\langle \widetilde{\mathbf{W}}_n, \boldsymbol{\xi} \rangle_{\mathcal{H}}
		\end{bmatrix}
		=
		\mathbf{Z} \mathbf{s}
		+
		\sum_{k=1}^K \widetilde{\mathbf{C}}^{(k)} \boldsymbol{\Phi}^{(k)} \mathbf{a}^{(k)}. 
	\end{equation*}
\end{definition}

@@

We now describe the strategy for computing the PLS direction at the $l$-th iteration. For simplicity, we omit the iteration index and denote the residualized response by $Y$, with finite-sample observations given by $\mathbf{y} = (y_1, \ldots, y_n) \in \mathbb{R}^n$. Let $\widetilde{W} \in \mathcal{H}$ denote the residualized, basis-approximated hybrid predictor, and let $\widetilde{\mathbf{C}}^{(1)}, \ldots, \widetilde{\mathbf{C}}^{(k)} \in \mathbb{R}^{n \times M}$ denote the basis coefficient matrices of its functional part in the finite-sample observations. Our strategy seeks the direction $\boldsymbol{\xi} \in \mathcal{H}$, whose functional parts lying in 
$\operatorname{span}(\Phi^{(1)}), \ldots, \operatorname{span}(\Phi^{(K)})$
, that maximizes the empirical covariance between the resulting PLS component $\langle \widetilde{W}, \boldsymbol{\xi} \rangle_{\mathcal{H}}$ and the response.

@@

	Now define a new operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}: \mathcal{H} \rightarrow \mathcal{H}$, which performs the following mapping:
	\begin{equation*}
		\mathcal{U} \mathbf{h} =  \mathcal{C}_{WY} ( \mathcal{C}_{YW} \mathbf{h}) 
		= \mathcal{C}_{YW} (\langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H}) 
		=  \Sigma_{YW} \, \langle \Sigma_{YW}, \mathbf{h} \rangle_\mathcal{H} = (\Sigma_{YW} \otimes \Sigma_{YW})\mathbf{h}.
	\end{equation*}
	In other words, $\mathcal{U} = \Sigma_{YW} \otimes \Sigma_{YW}$. The following proposition presents several important properties of $\mathcal{U}$.
	\begin{proposition} \label{Proposition: property of U}
		The operator $\mathcal{U} = \mathcal{C}_{WY} \circ \mathcal{C}_{YW}= \Sigma_{YW} \otimes \Sigma_{YW}: \mathcal{H} \rightarrow \mathcal{H}$ is positive and self-adjoint. Furthermore, if there exist finite constants $Q_1$ and $Q_2$ such that
		\begin{align}
			\max \limits_{k=1, \ldots, K} \sup \limits_{t_k \in \mathcal{T}_k} \sigma_{YX}^{(k)2}(t_k) < Q_1 \quad \textnormal{and} \quad  \max_{r=1, \ldots, p} \sigma_{YZ, r}^2 < Q_2,
		\end{align}
		and if each $\sigma_{YX}^{(k)}$ ($k=1, \ldots, K)$ is uniformly continuous in a sense that for any $\epsilon > 0$, there exists $\delta_k > 0$ such that for every $t_k,t^*_k \in \mathcal{T}_k$ with $|t_k - t_k^* | < \delta_k$, we have that
		\begin{equation*}
			|\sigma_{yx}^{(k)}(t_k) - \sigma_{yx}^{(k)}(t_k^*) | < \epsilon,
		\end{equation*}
		then $\mathcal{U}$ is a compact operator.
	\end{proposition}
	The proof of Proposition \ref{Proposition: property of U} is provided in Appendix \ref{section:proof:Proposition: property of U}.
	By the Hilbert-Schmidt theorem (e.g., Theorem 4.2.4 in \citealp{Hsing2015}), Proposition \ref{Proposition: property of U} guarantees the existence of a complete orthonormal system of eigenfunctions $\{\boldsymbol{\xi}_{(u)}\}_{u \in \mathbb{N}}$ of $\mathcal{U}$ in $\mathcal{H}$ such that $\mathcal{U} \boldsymbol{\xi}_{(u)} = \kappa_{(u)}  \boldsymbol{\xi}_{(u)}$, where $\{\kappa_{(u)}\}_{u \in \mathbb{N}}$ are the corresponding sequence of eigenvalues that goes to zero as $u \rightarrow \infty$, that is, $\kappa_{(1)} \ge \kappa_{(2)} \ge \cdots \ge 0$.

	The following proposition introduces the Tucker's Criterion adapted to our scalar-on-hybrid regression model setting based on the aformentioned operators defined in the hybrid space.
	\begin{proposition}\label{proposition: eigenanalysis}
		\begin{equation*}
			\max \limits_{\substack{\boldsymbol{\xi} \in \mathcal{H} \\ \Vert \boldsymbol{\xi} \Vert_\mathcal{H}=1}} \textnormal{Cov}^2 \left(\langle \mathbf{W}, \boldsymbol{\xi} \rangle_\mathcal{H}, Y \right)
		\end{equation*}
		is achieved when $\boldsymbol{\xi}$ is an eigenfunction associated with the largest eigenvalue of $\mathcal{U}$.	
	\end{proposition}
	The proof of Proposition \ref{proposition: eigenanalysis} is provided in Appendix \ref{section:proof:proposition: eigenanalysis}.
	In other words, $l$-th PLS component $\boldsymbol{\xi}_l$ can be obtained as the \textit{first} eigenfunction of $\mathcal{U}^{[l]} = \Sigma_{YW}^{[l]} \otimes \Sigma_{YW}^{[l]}$ whose components are formulated using the $l$-th residualized response and predictors: $\Sigma_{YW}^{[l]} = E(Y^{[l]} \mathbf{W}^{[l]})$.

@@

	The following proposition states that the PLS components estimated from Proposition  \ref{Proposition: Regularized generalized rayleigh quotient} are orthonormal with respect to the modified inner product $\langle \langle \cdot \rangle \rangle$ that incorporates the roughness of the functions.
	\begin{proposition}\label{proposition: modified orthnormality of PLS components}
		The estimated PLS components, $\widehat{\boldsymbol{\xi}}_1, \widehat{\boldsymbol{\xi}}_2, \ldots, \widehat{\boldsymbol{\xi}}_L$, from the proposed PLS algorithm are mutually orthonormal with respect to the modified inner product $\langle \langle h_l, h_j \rangle \rangle = \langle h_l, h_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \langle \ddot{f}_l^{(k)}, \ddot{f}_j^{(k)} \rangle_{L^2}$ in $\mathcal{H}$ that incorporates the roughness of the functions; i.e.,
		\begin{equation*}
			\langle \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle \rangle 
			= \langle \widehat{\boldsymbol{\xi}}_l, \widehat{\boldsymbol{\xi}}_j \rangle_{\mathcal{H}} + \sum_{k=1}^K \lambda_k \left\langle \ddot{\widehat{\psi}}_l^{(k)}, \ddot{\widehat{\psi}}_j^{(k)} \right\rangle_{L^2}
			= \mathbb{1}(l=j). 
		\end{equation*}
	\end{proposition}
	The proof of Proposition \ref{proposition: modified orthnormality of PLS components} is provided in Appendix \ref{section:proof:proposition: modified orthnormality of PLS components}.
	Now let $\widehat{\boldsymbol{\rho}}_l=(\widehat{\rho}_{1l}, \ldots, \widehat{\rho}_{nl})^\top$ denote the $n$-dimensional vector whose elements consist of estimated $l$-th PLS scores ($l=1, \ldots, L)$ of $n$ observations. The next proposition states that the vectors of estimated PLS scores $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$ obtained from the proposed algorithm are mutually orthogonal.
	\begin{proposition}	\label{proposition: orthnormality of PLS scores}
		The vectors of estimated PLS scores, $\widehat{\boldsymbol{\rho}}_1, \widehat{\boldsymbol{\rho}}_2, \ldots, \widehat{\boldsymbol{\rho}}_L$, obtained from the proposed PLS algorithm are mutually orthogonal in the sense that
		\begin{equation*}
			\widehat{\boldsymbol{\rho}}_l^\top \widehat{\boldsymbol{\rho}}_j= 0 \quad \textnormal{for} \quad \; l,j \in \{1, \ldots, L\}, \; l \ne j. 
		\end{equation*}
	\end{proposition}
The proof of Proposition \ref{proposition: orthnormality of PLS scores} is provided in Appendix \ref{section:proof:proposition: orthnormality of PLS scores}.

@@

	\section{Notations}
	\begin{itemize}
		\item aaa
	\end{itemize}
	\section{Technical lemmas}

	\subsection{old notations}

	Then we can approximate the functional predictor observations as
	\begin{equation*}
		X_i^{(k)}(t_k) = \sum_{m=1}^M c_{im}^{(k)} b^{(k)}_{m}(t_k)=\mathbf{c}_i^{(k)T}\mathbf{b}^{(k)}(t_k), \;\; t_k \in \mathcal{T}_k, \;\; k=1, \ldots, K, \;\; i=1, \ldots, n,
	\end{equation*}
 This basis approximation can be expressed collectively across $n$ observations as: $\widetilde{\mathbf{X}^{(k)}}(t_k) = \widetilde{\mathbf{C}}^{(k)} \mathbf{b}^{(k)}(t_k)$, where $\widetilde{\mathbf{X}}^{(k)}(t_k)=(X_1^{(k)}(t_k), \ldots, X_n^{(k)}(t_k))^\top \in \mathbb{R}^n$, 
 This notation can be further extended to simultaneously express the basis expansions of $K$ functional predictors as 
	\begin{equation}
		\widetilde{X}(\mathbf{t}) = \widetilde{C}B(\mathbf{t}), \quad t \in \mathcal{T},
		\label{eq: basis approximation of X}
	\end{equation}
	where $\widetilde{X}(\mathbf{t}) = [\widetilde{\mathbf{X}}^{(1)}(t_1), \cdots, \widetilde{\mathbf{X}}^{(K)}(t_K)] \in \mathbb{R}^{n \times K}$, $\widetilde{C} = [\widetilde{C}^{(1)}, \cdots, \widetilde{\mathbf{C}}^{(k)}] \in \mathbb{R}^{n \times MK}$, and 
	$B(\mathbf{t}) = \mathrm{blkdiag}[\mathbf{b}^{(1)}(t_1), \cdots, \mathbf{b}^{(K)}(t_K)] \in \mathbb{R}^{MK \times K}$.
